Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

We now solve the $(k-2)$-SJ problem on $R_1', R_2', ..., R_{k-2}'$ using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-2)$-SJ clearly has an input size at most $n$, and let us represent its result as $\J(R'_1, R'_2, ..., R'_{k-2})$. We prove in Appendix~\ref{app:hv}:

%The lemma below shows that the result is essentially what we aim to compute in Step 1.

@@

% \begin{figure}
%     \includegraphics[height=30mm]{./artwork/four-segs}
%     \figcapup
%     \caption{Trimming}
%     \label{fig:hv:type1:trim}
%     \figcapdown
% \end{figure}

\extraspacing {\bf Generating $\bm{\J^*}$.} Take any $(k-2)$-tuple $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2}) \in \J(R_1', R'_2, ..., R'_{k-2})$. The reader should recall from Section~\ref{sec:bricks} that
\myitems{
    \item $B_\bm{t}$ is $\bigcap_{i=1}^{k-2} \bm{t}[i] = \bigcap_{i=1}^{k-2} r'_i$;
    \item $\gleft(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\xleft(r'_i) = \xleft(B_\bm{t})$;
    \item $\gbot(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\ybot(r'_i) = \ybot(B_\bm{t})$.
}
We now introduce:
% \myitems{
%     \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$;
%     \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
% }
\myeqn{
    \dcross_H(\bm{t}) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}} \label{eqn:dcross-H} \\
    \dcross_V(\bm{t}) = \set{v \in V \mid \text{$v$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}}. \nn
    %\label{eqn:dcross-H} 
}
The prefix ``d-'' stands for ``double''. These sets have important properties as stated in the next lemma, whose proof can be found in Appendix~\ref{app:hv}:

@@

\extraspacing {\bf Set $\bm{H'}$.}

@@

>>>>

We now solve a $(k-2)$-SJ problem with $R_1', R_2', ..., R_{k-2}'$ as the input using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-2)$-SJ clearly has an input size at most $n$, and let us represent its result as $\J(R'_1, R'_2, ..., R'_{k-2})$. We prove in Appendix~\ref{app:hv}:

@@

\extraspacing {\bf Generating $\bm{\J^*}$.} Take any $(k-2)$-tuple $\bm{t} = (r'_1, r'_2, ...,$ $r'_{k-2}) \in \J(R_1', R'_2, ..., R'_{k-2})$. The reader should recall from Section~\ref{sec:bricks} that
\myitems{
    \item $B_\bm{t}$ is $\bigcap_{i=1}^{k-2} \bm{t}[i] = \bigcap_{i=1}^{k-2} r'_i$;
    \item $\gleft(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\xleft(r'_i) = \xleft(B_\bm{t})$;
    \item $\gbot(\bm{t})$ is the $r'_i$ ($1 \le i \le k-2$) with $\ybot(r'_i) = \ybot(B_\bm{t})$.
}
We now introduce:
\myeqn{
    \dcross_H(\bm{t}) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}} \label{eqn:dcross-H} \\
    \dcross_V(\bm{t}) = \set{v \in V \mid \text{$v$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}}. \nn
    %\label{eqn:dcross-H} 
}
The prefix ``d-'' stands for ``double''. These sets have important properties as stated in the next lemma, whose proof can be found in Appendix~\ref{app:hv}:

@@

\extraspacing {\bf Set $\bm{H'}$.} For each horizontal segment $h = [x_1, x_2] \times y \in H$, we want to find the rightmost point $p$ on $h$, such that $p$ is covered by at least one rectangle $r_{k-2} \in R_{k-2}$. This point $p$ exists if and only if $h$ has at least one left-end covering rectangle in $R_{k-2}$. If $p$ exists and has coordinates $(x, y)$, we construct a segment $h' = [x_1, x] \times y$,  referred to as the {\em trimmed segment} of $h$; conversely, we call $h$ the {\em full segment} of $h'$.

Construct
\myeqn{
    H' &=& \{h' \mid h \in H \text{ and its trimmed segment $h'$ exists} \}. \nn
}
The construction requires solving an instance of Problem $\mathscr{C}$, which takes $O(n \log n)$ time based on the discussion in Section~\ref{sec:bricks}.

We now solve a $(k-1)$-SJ problem with $R_1, ..., R_{k-1}, H', V$ as the input using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-1)$-SJ has an input size at most $n$, and let us represent its result as $\J(R_1, R_2, ..., R_{k-1}, H', V)$. We prove in Appendix~\ref{app:hv}:

\begin{lemma} \label{lmm:hv:type2:recur-output}
    $|\J(R_1, ..., R_{k-1}, H', V)| \le \out$.
\end{lemma}

@@

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type2:recur-output}.}
